Notebook of learning from ensemble labels

### 2021-06-09 docs/notebook_learn_dl_ensemble.Rmd
A few updates for test

```
python hrlcm/fit.py --exp_name unet_single --data_dir 'results/north' --out_dir 'results/dl' --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200
```

@@

#### JoCoR

@@

- Learning rate and learning rate scheduler
- Batch size
- Optimizer
- Model (Unet or Deeplab)
- Transform methods (if necessary)

@@

### Resume

#### Single model

#### Double model

>>>>

```
python hrlcm/fit_coteaching_compare.py --exp_name unet_cot_argue --num_workers 32 --gpu_devices '0,1,2,3' --epochs 30
```

```
python hrlcm/fit_coteaching.py --exp_name unet_cot_da --num_workers 32 --gpu_devices '0,1,2,3' --save_freq 5 --resume1 'results/dl/unet_cot_da/model1_final.pth' --resume2 'results/dl/unet_cot_da/model2_final.pth'
```

@@

Based on the original papers and their GitHub repos, we combined these two logic into one function and adapted it for image segmentation.

- The first version is image based, which means it takes each image as a whole thing. If the label of one image is "perfect", then use the whole image, otherwise only use pixels with small loss to update the models.
  - Under "argue" mode, use disagreement to update the models.
  - Under "discuss" mode, do not use disagreement.

- The second version is batch based, which means it only use pixels with small loss from the whole batch to update the models. Mode works similarly as the first version.

#### JoCoR
Since the original paper is about image classification rather than image segmentation, it is harder to adapt this method into image segmentation with good performance.

[NEED MORE EXPERIMENTS]

@@

- <input type="checkbox" checked> Learning rate and learning rate scheduler</input>
- Batch size
- Optimizer
- Model (U-net or Deeplab)
- Transform methods (if necessary)

@@

### Co-teaching

We first use constant parameters, 0.001 learning rate, AmsBound optimizer, and 30 epochs, to run the models.

- Co_teaching_batch doesn't fit multi-classes classification task. It might be good for binary classification. Because based on the curves, co_teaching_batch give up the minorities.

- Co_teaching works good. "Discuss" mode works slightly better than "argue" mode.
